Learning to Estimate Search Progress Using Graph Neural Networks \thanks{This work expands on \citet{sudry2022learning}.}

### 2024-11-05 report/submission.tex
report run times, scores by sets, and fix readme

For each problem instance, we ran $A^{\star}$ search with all three domain-specific heuristics, recording detailed information about the search process. Each node in the resulting search graphs contains:
\begin{itemize}
    \item Search featuresas described in \nameref{para:learning-to-estimate}.
    \item Search trajectory information (parent node, children count).
    \item The desired prediction - search progress ($\frac{\text{serial number}}{\text{total nodes}}$).
\end{itemize}

@@

\begin{table}[t]
    \centering
    \caption{Performance comparison of different approaches}
    \label{tab:performance}
    \begin{tabular}{|l|c|c|}
    \hline
    \textbf{Model} & \textbf{MSE} & \textbf{Inference Time [s]}\\
    \hline
    VeSP & 0.1605 & 11.14 \\
    VaSP & 0.0569 & 18.69 \\
    PBP & 0.0379 & 9.55 \\
    Random Forest & 0.0328 & 10.02 \\
    HeavyGNN & 0.00193 & \\
    LightGNN & 0.00151 & \\
    \hline
    \end{tabular}
\end{table}

>>>>

For each problem instance, we ran $A^{\star}$ search with all three domain-specific heuristics, recording detailed information about the search process. Each node in the resulting search graphs contains:
\begin{itemize}
    \item Search features as described in \nameref{para:learning-to-estimate}.
    \item Search trajectory information (parent node, children count).
    \item The desired prediction - search progress ($\frac{\text{serial number}}{\text{total nodes}}$).
\end{itemize}

@@

\begin{table}[t]
    \centering
    \caption{MSE of GNN Models on Training, Validation \& Test Sets}
    \label{tab:train-test}
    \begin{tabular}{|l|c|c|c|}
    \hline
    \textbf{Model} & \textbf{Train} & \textbf{Validation} & \textbf{Test} \\
    \hline
    HeavyGNN & 0.0013 & 0.0016 & 0.001929 \\  
    LightGNN & 0.0016 & 0.0015 & 0.001507 \\    
    \hline
    \end{tabular}
\end{table}

\begin{table}[t]
    \centering
    \caption{Performance comparison of different approaches on the full dataset}
    \label{tab:performance}
    \begin{tabular}{|l|c|c|}
    \hline
    \textbf{Model} & \textbf{MSE} & \textbf{Inference Time [s]}\\
    \hline
    VeSP & 0.1605 & 11.14 \\
    VaSP & 0.0569 & 18.69 \\
    PBP & 0.0379 & 9.55 \\
    Random Forest & 0.0328 & 10.02 \\
    HeavyGNN & 0.000982 & 72.94 \\ 
    LightGNN & 0.001142 & 44.48 \\ 
    \hline
    \end{tabular}
\end{table}
